---
title: "ZCTC_LCMC"
author: "Jiajun"
date: "2026-05-02"
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    code_folding: show
---
# Load packages
```{r}
library(xml2)
library(openxlsx)
library(readr)
```

# ZCTC corpus genre list
## Set the folder path
```{r}
folder_path <- "D:/NLPtools/ZCTC WordSmith edition"
```

## Get all .txt files in the folder
```{r}
txt_files <- list.files(path = folder_path, pattern = "\\.txt$", full.names = TRUE)
```

## Create an empty results table
```{r}
genre_data <- data.frame(FileID = character(), Genre = character(), stringsAsFactors = FALSE)
```

## Extract file and genre names
```{r}
for (file in txt_files) {
  file_name <- tools::file_path_sans_ext(basename(file))  
  
  xml_text <- read_file(file, locale = locale(encoding = "UTF-16LE"))
  
  tryCatch({
    doc <- read_xml(xml_text)
    genre <- xml_attr(xml_find_first(doc, "//cesDoc"), "genre")
    genre <- trimws(genre)  
  })
  
  genre_data <- rbind(genre_data, data.frame(FileID = file_name, Genre = genre, stringsAsFactors = FALSE))
}
```

## Save the results to Excel
```{r}
output_path <- file.path(folder_path, "ZCTC_genre_list.xlsx")
write.xlsx(genre_data, file = output_path, rowNames = FALSE)
```

# LCMC corpus genre list
## Set the folder path
```{r}
folder_path <- "D:/NLPtools/LCMCv2 WordSmith edition"
```

## Get all .txt files in the folder
```{r}
txt_files <- list.files(path = folder_path, pattern = "\\.txt$", full.names = TRUE)
```

## Create an empty results table
```{r}
genre_data <- data.frame(FileID = character(), Genre = character(), stringsAsFactors = FALSE)
```

## Extract file and genre names
```{r}
for (file in txt_files) {
  file_name <- tools::file_path_sans_ext(basename(file))  
  

  xml_text <- read_file(file, locale = locale(encoding = "UTF-16LE"))
  

  tryCatch({
    doc <- read_xml(xml_text)
    genre <- xml_attr(xml_find_first(doc, "//cesDoc"), "genre")
    genre <- trimws(genre)  
  })
  
  genre_data <- rbind(genre_data, data.frame(FileID = file_name, Genre = genre, stringsAsFactors = FALSE))
}
```

## Save the results to Excel
```{r}
output_path <- file.path(folder_path, "LCMC_genre_list.xlsx")
write.xlsx(genre_data, file = output_path, rowNames = FALSE)
```

# Clean data
## removing tags in ZCTC corpus and controlling for the number of tokens

### Load packages
```{r}
library(xml2)
library(stringr)
library(readr)
```

### Set the folder path
```{r}
folder_path <- "D:/NLPtools/ZCTC WordSmith edition"
```

## Get all .txt files
```{r}
txt_files <- list.files(path = folder_path, pattern = "\\.txt$", full.names = TRUE)
```

## Extract sentences and remove tags
```{r}
for (file in txt_files) {
  # Extract the original file name without the extension
  base_name <- tools::file_path_sans_ext(basename(file))
  
  # Set the output file name: ZCTC_A01_raw.txt
  output_file <- file.path(folder_path, paste0(base_name, "_raw.txt"))
  
  # Read and parse the UTF-16 XML content
  xml_text <- read_file(file, locale = locale(encoding = "UTF-16LE"))
  doc <- read_xml(xml_text)
  
  # Extract the content of all <s> elements
  sentences <- xml_find_all(doc, ".//s")
  
  # Initialize the sentence list
  clean_sentences <- c()
  
  for (s in sentences) {
    raw <- xml_text(s)  # Example: 戴维·麦克林_nrf 时_ng ...
    cleaned <- str_replace_all(raw, "_[^\\s]+", "")  # Remove part-of-speech tags
    cleaned <- str_squish(cleaned)  # Remove extra spaces
    clean_sentences <- c(clean_sentences, cleaned)
  }
  
  # Save to the corresponding _raw.txt file
  writeLines(clean_sentences, output_file, useBytes = TRUE)
  cat("Generated:", output_file, "\n")
}
```

## Trimming ZCTC raw files
```{r}
library(stringr)
library(readr)

# Set the folder path
folder_path <- "D:/NLPtools/ZCTC WordSmith edition"

# Get all _raw.txt files
raw_files <- list.files(
  path = folder_path,
  pattern = "_raw\\.txt$",
  full.names = TRUE
)

# Set output folder
output_folder <- file.path(folder_path, "clean1500")
dir.create(output_folder, showWarnings = FALSE)

# Remove old clean1500 files to avoid mixing old and new results
old_files <- list.files(
  path = output_folder,
  pattern = "_clean1500\\.txt$",
  full.names = TRUE
)

if (length(old_files) > 0) {
  unlink(old_files)
}

# Function: merge separated English letters
merge_letter_run <- function(run) {
  n <- length(run)
  
  if (n == 1) {
    return(run)
  }
  
  is_upper <- str_detect(run, "^[A-Z]$")
  is_lower <- str_detect(run, "^[a-z]$")
  
  # Example: V C -> VC
  if (all(is_upper)) {
    return(paste0(run, collapse = ""))
  }
  
  parts <- character(0)
  i <- 1
  
  while (i <= n) {
    
    if (is_upper[i]) {
      
      # Example: O r a c l e -> Oracle
      # Example: M e n l o -> Menlo
      if (i < n && is_lower[i + 1]) {
        j <- i + 1
        
        while (j <= n && is_lower[j]) {
          j <- j + 1
        }
        
        parts <- c(parts, paste0(run[i:(j - 1)], collapse = ""))
        i <- j
        
      } else {
        
        # Example: U S V e n t u r e -> US Venture
        j <- i
        
        while (
          j <= n &&
          is_upper[j] &&
          !(j < n && is_lower[j + 1])
        ) {
          j <- j + 1
        }
        
        parts <- c(parts, paste0(run[i:(j - 1)], collapse = ""))
        i <- j
      }
      
    } else {
      
      # Merge lowercase letter sequences if they occur
      j <- i
      
      while (j <= n && is_lower[j]) {
        j <- j + 1
      }
      
      parts <- c(parts, paste0(run[i:(j - 1)], collapse = ""))
      i <- j
    }
  }
  
  return(parts[parts != ""])
}

# Function: scan tokens and merge separated English letters
merge_spaced_english_letters <- function(tokens) {
  result <- character(0)
  i <- 1
  n <- length(tokens)
  
  while (i <= n) {
    
    if (str_detect(tokens[i], "^[A-Za-z]$")) {
      j <- i
      
      while (j <= n && str_detect(tokens[j], "^[A-Za-z]$")) {
        j <- j + 1
      }
      
      letter_run <- tokens[i:(j - 1)]
      merged <- merge_letter_run(letter_run)
      
      result <- c(result, merged)
      i <- j
      
    } else {
      result <- c(result, tokens[i])
      i <- i + 1
    }
  }
  
  return(result)
}

# Record excluded files
excluded_files <- data.frame(
  FileID = character(),
  WordCountAfterCleaning = integer(),
  stringsAsFactors = FALSE
)

# Record saved files
saved_files <- data.frame(
  FileID = character(),
  WordCountBeforeTruncation = integer(),
  FinalWordCount = integer(),
  stringsAsFactors = FALSE
)

# Process each _raw.txt file
for (file in raw_files) {
  
  # Extract file name
  base_name <- tools::file_path_sans_ext(basename(file))
  base_name <- str_replace(base_name, "_raw$", "")
  
  # Set output file name
  output_file <- file.path(output_folder, paste0(base_name, "_clean1500.txt"))
  
  # Read raw text
  text <- read_file(file, locale = locale(encoding = "UTF-8"))
  
  # Remove punctuation and numbers
  text <- str_replace_all(text, "[\\p{P}\\p{N}]+", " ")
  
  # Remove extra spaces
  text <- str_squish(text)
  
  # If the file becomes empty after cleaning, exclude it
  if (text == "") {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = base_name,
        WordCountAfterCleaning = 0,
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", base_name, "- 0 words after cleaning\n")
    next
  }
  
  # Split into tokens
  tokens <- unlist(str_split(text, "\\s+"))
  tokens <- tokens[tokens != ""]
  
  # Merge separated English letters
  tokens <- merge_spaced_english_letters(tokens)
  
  # Remove empty tokens again
  tokens <- tokens[tokens != ""]
  
  # Count words after punctuation/number removal and English-letter merging
  word_count <- length(tokens)
  
  # Exclude files with fewer than 1500 words
  if (word_count < 1500) {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = base_name,
        WordCountAfterCleaning = word_count,
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", base_name, "-", word_count, "words after cleaning\n")
    next
  }
  
  # Keep only the first 1500 words
  tokens_1500 <- tokens[1:1500]
  
  # Save cleaned 1500-word file
  write_lines(paste(tokens_1500, collapse = " "), output_file)
  
  # Record saved file information
  saved_files <- rbind(
    saved_files,
    data.frame(
      FileID = base_name,
      WordCountBeforeTruncation = word_count,
      FinalWordCount = length(tokens_1500),
      stringsAsFactors = FALSE
    )
  )
  
  cat("Saved:", base_name, "-", word_count, "words before truncation; 1500 words saved\n")
}

# Save records
excluded_path <- file.path(output_folder, "excluded_files.csv")
saved_path <- file.path(output_folder, "saved_files.csv")

write_csv(excluded_files, excluded_path)
write_csv(saved_files, saved_path)

cat("\nCleaning completed.\n")
cat("Cleaned files saved in:", output_folder, "\n")
cat("Excluded file list saved to:", excluded_path, "\n")
cat("Saved file list saved to:", saved_path, "\n")
```

## Check the number of tokens
```{r}
library(stringr)
library(readr)

output_folder <- "D:/NLPtools/ZCTC WordSmith edition/clean1500"

clean_files <- list.files(
  path = output_folder,
  pattern = "_clean1500\\.txt$",
  full.names = TRUE
)

check_counts <- data.frame(
  FileID = character(),
  WordCount = integer(),
  stringsAsFactors = FALSE
)

for (file in clean_files) {
  text <- read_file(file, locale = locale(encoding = "UTF-8"))
  tokens <- unlist(str_split(str_squish(text), "\\s+"))
  tokens <- tokens[tokens != ""]
  
  check_counts <- rbind(
    check_counts,
    data.frame(
      FileID = basename(file),
      WordCount = length(tokens),
      stringsAsFactors = FALSE
    )
  )
}

print(check_counts)

# Show files that are not exactly 1500 words
problem_files <- check_counts[check_counts$WordCount != 1500, ]
print(problem_files)
```

## removing tags in LCMC corpus and controlling for the number of tokens

### Load packages
```{r}
library(xml2)
library(stringr)
library(readr)
```

### Set the folder path
```{r}
folder_path <- "D:/NLPtools/LCMCv2 WordSmith edition"
```

## Get all .txt files
```{r}
txt_files <- list.files(path = folder_path, pattern = "\\.txt$", full.names = TRUE)
```

## Extract sentences and remove tags
```{r}
for (file in txt_files) {
  # Extract the original file name without the extension
  base_name <- tools::file_path_sans_ext(basename(file))
  
  # Set the output file name: ZCTC_A01_raw.txt
  output_file <- file.path(folder_path, paste0(base_name, "_raw.txt"))
  
  # Read and parse the UTF-16 XML content
  xml_text <- read_file(file, locale = locale(encoding = "UTF-16LE"))
  doc <- read_xml(xml_text)
  
  # Extract the content of all <s> elements
  sentences <- xml_find_all(doc, ".//s")
  
  # Initialize the sentence list
  clean_sentences <- c()
  
  for (s in sentences) {
    raw <- xml_text(s)  # Example: 戴维·麦克林_nrf 时_ng ...
    cleaned <- str_replace_all(raw, "_[^\\s]+", "")  # Remove part-of-speech tags
    cleaned <- str_squish(cleaned)  # Remove extra spaces
    clean_sentences <- c(clean_sentences, cleaned)
  }
  
  # Save to the corresponding _raw.txt file
  writeLines(clean_sentences, output_file, useBytes = TRUE)
  cat("Generated:", output_file, "\n")
}
```
## Trimming LCMC raw files
```{r}
library(stringr)
library(readr)

# Set the folder path for LCMC
folder_path <- "D:/NLPtools/LCMCv2 WordSmith edition"

# Get all _raw.txt files
raw_files <- list.files(
  path = folder_path,
  pattern = "_raw\\.txt$",
  full.names = TRUE
)

cat("Number of _raw.txt files found:", length(raw_files), "\n")

# Set output folder
output_folder <- file.path(folder_path, "clean1500")
dir.create(output_folder, showWarnings = FALSE)

# Remove old clean1500 files to avoid mixing old and new results
old_files <- list.files(
  path = output_folder,
  pattern = "_clean1500\\.txt$",
  full.names = TRUE
)

if (length(old_files) > 0) {
  unlink(old_files)
}

# Function: merge separated English letters
merge_letter_run <- function(run) {
  n <- length(run)
  
  if (n == 1) {
    return(run)
  }
  
  is_upper <- str_detect(run, "^[A-Z]$")
  is_lower <- str_detect(run, "^[a-z]$")
  
  # Example: V C -> VC
  if (all(is_upper)) {
    return(paste0(run, collapse = ""))
  }
  
  parts <- character(0)
  i <- 1
  
  while (i <= n) {
    
    if (is_upper[i]) {
      
      # Example: O r a c l e -> Oracle
      # Example: M e n l o -> Menlo
      if (i < n && is_lower[i + 1]) {
        j <- i + 1
        
        while (j <= n && is_lower[j]) {
          j <- j + 1
        }
        
        parts <- c(parts, paste0(run[i:(j - 1)], collapse = ""))
        i <- j
        
      } else {
        
        # Example: U S V e n t u r e -> US Venture
        j <- i
        
        while (
          j <= n &&
          is_upper[j] &&
          !(j < n && is_lower[j + 1])
        ) {
          j <- j + 1
        }
        
        parts <- c(parts, paste0(run[i:(j - 1)], collapse = ""))
        i <- j
      }
      
    } else {
      
      # Merge lowercase letter sequences if they occur
      j <- i
      
      while (j <= n && is_lower[j]) {
        j <- j + 1
      }
      
      parts <- c(parts, paste0(run[i:(j - 1)], collapse = ""))
      i <- j
    }
  }
  
  return(parts[parts != ""])
}

# Function: scan tokens and merge separated English letters
merge_spaced_english_letters <- function(tokens) {
  result <- character(0)
  i <- 1
  n <- length(tokens)
  
  while (i <= n) {
    
    if (str_detect(tokens[i], "^[A-Za-z]$")) {
      j <- i
      
      while (j <= n && str_detect(tokens[j], "^[A-Za-z]$")) {
        j <- j + 1
      }
      
      letter_run <- tokens[i:(j - 1)]
      merged <- merge_letter_run(letter_run)
      
      result <- c(result, merged)
      i <- j
      
    } else {
      result <- c(result, tokens[i])
      i <- i + 1
    }
  }
  
  return(result)
}

# Record excluded files
excluded_files <- data.frame(
  FileID = character(),
  WordCountAfterCleaning = integer(),
  stringsAsFactors = FALSE
)

# Record saved files
saved_files <- data.frame(
  FileID = character(),
  WordCountBeforeTruncation = integer(),
  FinalWordCount = integer(),
  stringsAsFactors = FALSE
)

# Stop if no _raw.txt files are found
if (length(raw_files) == 0) {
  stop("No _raw.txt files were found. Please check the LCMC folder path.")
}

# Process each _raw.txt file
for (file in raw_files) {
  
  # Extract file name
  base_name <- tools::file_path_sans_ext(basename(file))
  base_name <- str_replace(base_name, "_raw$", "")
  
  # Set output file name
  output_file <- file.path(output_folder, paste0(base_name, "_clean1500.txt"))
  
  # Read raw text
  text <- read_file(file, locale = locale(encoding = "UTF-8"))
  
  # Remove punctuation and numbers
  text <- str_replace_all(text, "[\\p{P}\\p{N}]+", " ")
  
  # Remove extra spaces
  text <- str_squish(text)
  
  # Exclude empty files
  if (text == "") {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = base_name,
        WordCountAfterCleaning = 0,
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", base_name, "- 0 words after cleaning\n")
    next
  }
  
  # Split into tokens
  tokens <- unlist(str_split(text, "\\s+"))
  tokens <- tokens[tokens != ""]
  
  # Merge separated English letters
  tokens <- merge_spaced_english_letters(tokens)
  
  # Remove empty tokens again
  tokens <- tokens[tokens != ""]
  
  # Count words after cleaning
  word_count <- length(tokens)
  
  # Exclude files with fewer than 1500 words
  if (word_count < 1500) {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = base_name,
        WordCountAfterCleaning = word_count,
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", base_name, "-", word_count, "words after cleaning\n")
    next
  }
  
  # Keep only the first 1500 words
  tokens_1500 <- tokens[1:1500]
  
  # Save cleaned 1500-word file
  write_lines(paste(tokens_1500, collapse = " "), output_file)
  
  # Record saved file information
  saved_files <- rbind(
    saved_files,
    data.frame(
      FileID = base_name,
      WordCountBeforeTruncation = word_count,
      FinalWordCount = length(tokens_1500),
      stringsAsFactors = FALSE
    )
  )
  
  cat("Saved:", base_name, "-", word_count, "words before truncation; 1500 words saved\n")
}

# Save records
excluded_path <- file.path(output_folder, "excluded_files.csv")
saved_path <- file.path(output_folder, "saved_files.csv")

write_csv(excluded_files, excluded_path)
write_csv(saved_files, saved_path)

cat("\nCleaning completed.\n")
cat("Cleaned files saved in:", output_folder, "\n")
cat("Excluded file list saved to:", excluded_path, "\n")
cat("Saved file list saved to:", saved_path, "\n")
```
## Check the number of tokens
```{r}
library(stringr)
library(readr)

output_folder <- "D:/NLPtools/LCMCv2 WordSmith edition/clean1500"

clean_files <- list.files(
  path = output_folder,
  pattern = "_clean1500\\.txt$",
  full.names = TRUE
)

check_counts <- data.frame(
  FileID = character(),
  WordCount = integer(),
  stringsAsFactors = FALSE
)

for (file in clean_files) {
  text <- read_file(file, locale = locale(encoding = "UTF-8"))
  tokens <- unlist(str_split(str_squish(text), "\\s+"))
  tokens <- tokens[tokens != ""]
  
  check_counts <- rbind(
    check_counts,
    data.frame(
      FileID = basename(file),
      WordCount = length(tokens),
      stringsAsFactors = FALSE
    )
  )
}

print(check_counts)

# Show files that are not exactly 1500 words
problem_files <- check_counts[check_counts$WordCount != 1500, ]
print(problem_files)
```

### ZCTC word entropy
```{r}
library(quanteda)
library(quanteda.textstats)
library(openxlsx)
library(stringr)

# Set the folder path to the clean1500 folder
folder_path <- "D:/NLPtools/ZCTC WordSmith edition/clean1500"

# Get all .txt files in the clean1500 folder
txt_files <- list.files(
  path = folder_path,
  pattern = "\\.txt$",
  full.names = TRUE
)

# Initialize the result data frame
entropy_results <- data.frame(
  FileID = character(),
  WRDentropy = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each cleaned txt file
for (file in txt_files) {
  
  # Extract file ID
  # Example: ZCTC_A01_clean1500.txt -> ZCTC_A01
  file_id <- basename(file)
  file_id <- str_replace(file_id, "_clean1500\\.txt$", "")
  file_id <- str_replace(file_id, "\\.txt$", "")
  
  # Read text content
  text <- readLines(file, warn = FALSE, encoding = "UTF-8")
  text <- paste(text, collapse = " ")
  
  # Create corpus
  corpus_obj <- corpus(text)
  
  # Tokenize the text
  toks <- tokens(corpus_obj, remove_punct = TRUE)
  
  # Create document-feature matrix
  dfmat <- dfm(toks)
  
  # Calculate word entropy
  entropy_val <- textstat_entropy(dfmat)$entropy
  
  # Add result
  entropy_results <- rbind(
    entropy_results,
    data.frame(
      FileID = file_id,
      WRDentropy = entropy_val,
      stringsAsFactors = FALSE
    )
  )
}

# Save results to Excel
output_path <- file.path(folder_path, "ZCTC_clean1500_WRDentropy_results.xlsx")

write.xlsx(
  entropy_results,
  file = output_path,
  rowNames = FALSE
)

cat("WRDentropy calculation completed. Results saved to:", output_path, "\n")
```

### LCMC word entropy
```{r}
library(quanteda)
library(quanteda.textstats)
library(openxlsx)
library(stringr)

# Set the folder path to the LCMC clean1500 folder
folder_path <- "D:/NLPtools/LCMCv2 WordSmith edition/clean1500"

# Get all .txt files in the clean1500 folder
txt_files <- list.files(
  path = folder_path,
  pattern = "\\.txt$",
  full.names = TRUE
)

# Initialize the result data frame
entropy_results <- data.frame(
  FileID = character(),
  WRDentropy = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each cleaned txt file
for (file in txt_files) {
  
  # Extract file ID
  # Example: LCMC_A01_clean1500.txt -> LCMC_A01
  file_id <- basename(file)
  file_id <- str_replace(file_id, "_clean1500\\.txt$", "")
  file_id <- str_replace(file_id, "\\.txt$", "")
  
  # Read text content
  text <- readLines(file, warn = FALSE, encoding = "UTF-8")
  text <- paste(text, collapse = " ")
  
  # Create corpus
  corpus_obj <- corpus(text)
  
  # Tokenize the text
  toks <- tokens(corpus_obj, remove_punct = TRUE)
  
  # Create document-feature matrix
  dfmat <- dfm(toks)
  
  # Calculate word entropy
  entropy_val <- textstat_entropy(dfmat)$entropy
  
  # Add result
  entropy_results <- rbind(
    entropy_results,
    data.frame(
      FileID = file_id,
      WRDentropy = entropy_val,
      stringsAsFactors = FALSE
    )
  )
}

# Save results to Excel
output_path <- file.path(folder_path, "LCMC_clean1500_WRDentropy_results.xlsx")

write.xlsx(
  entropy_results,
  file = output_path,
  rowNames = FALSE
)

cat("LCMC WRDentropy calculation completed. Results saved to:", output_path, "\n")
```

# ZCTC POS
## Cleaning ZCTC for pos tags
```{r}
library(xml2)
library(stringr)
library(readr)
library(openxlsx)

# Set the folder path
folder_path <- "D:/NLPtools/ZCTC WordSmith edition"

# Get original .txt XML files
txt_files <- list.files(
  path = folder_path,
  pattern = "\\.txt$",
  full.names = TRUE
)

# Exclude files generated in previous steps
txt_files <- txt_files[
  !str_detect(txt_files, "_raw\\.txt$") &
  !str_detect(txt_files, "_clean1500\\.txt$")
]

# Set output folder
output_folder <- file.path(folder_path, "pos1500")
dir.create(output_folder, showWarnings = FALSE)

# Remove old POS output files
old_files <- list.files(
  path = output_folder,
  pattern = "_pos1500\\.txt$",
  full.names = TRUE
)

if (length(old_files) > 0) {
  unlink(old_files)
}

# Create records
saved_files <- data.frame(
  FileID = character(),
  POSTagCountBeforeTruncation = integer(),
  FinalPOSTagCount = integer(),
  stringsAsFactors = FALSE
)

excluded_files <- data.frame(
  FileID = character(),
  POSTagCount = integer(),
  Reason = character(),
  stringsAsFactors = FALSE
)

# Process each file
for (file in txt_files) {
  
  # Extract file ID
  file_id <- tools::file_path_sans_ext(basename(file))
  
  # Set output file name
  output_file <- file.path(output_folder, paste0(file_id, "_pos1500.txt"))
  
  # Read and parse UTF-16 XML content
  xml_text_content <- read_file(file, locale = locale(encoding = "UTF-16LE"))
  
  doc <- tryCatch(
    read_xml(xml_text_content),
    error = function(e) NULL
  )
  
  if (is.null(doc)) {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = file_id,
        POSTagCount = 0,
        Reason = "XML parsing failed",
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", file_id, "- XML parsing failed\n")
    next
  }
  
  # Extract all <s> elements
  sentences <- xml_find_all(doc, ".//s")
  
  # Initialize POS tag vector
  pos_tags <- c()
  
  for (s in sentences) {
    
    # Extract sentence text
    raw <- xml_text(s)
    
    # Split sentence into word_POS tokens
    tokens <- unlist(str_split(str_squish(raw), "\\s+"))
    tokens <- tokens[tokens != ""]
    
    # Process each token
    for (tok in tokens) {
      
      # Keep only tokens containing an underscore
      if (!str_detect(tok, "_")) {
        next
      }
      
      # Extract word and POS tag
      word <- str_replace(tok, "_[^_]+$", "")
      pos <- str_extract(tok, "(?<=_)[^_\\s]+$")
      
      # Remove punctuation tokens
      if (str_detect(word, "^[\\p{P}]+$")) {
        next
      }
      
      # Remove empty POS tags
      if (is.na(pos) || pos == "") {
        next
      }
      
      # Keep POS tag
      pos_tags <- c(pos_tags, pos)
    }
  }
  
  # Count POS tags
  pos_count <- length(pos_tags)
  
  # Exclude files with fewer than 1500 POS tags
  if (pos_count < 1500) {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = file_id,
        POSTagCount = pos_count,
        Reason = "Fewer than 1500 POS tags",
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", file_id, "-", pos_count, "POS tags\n")
    next
  }
  
  # Keep only the first 1500 POS tags
  pos_tags_1500 <- pos_tags[1:1500]
  
  # Save POS tags
  write_lines(paste(pos_tags_1500, collapse = " "), output_file)
  
  # Record saved files
  saved_files <- rbind(
    saved_files,
    data.frame(
      FileID = file_id,
      POSTagCountBeforeTruncation = pos_count,
      FinalPOSTagCount = length(pos_tags_1500),
      stringsAsFactors = FALSE
    )
  )
  
  cat("Saved:", file_id, "-", pos_count, "POS tags before truncation; 1500 POS tags saved\n")
}

# Save records
saved_path <- file.path(output_folder, "ZCTC_saved_pos1500_files.xlsx")
excluded_path <- file.path(output_folder, "ZCTC_excluded_pos_files.xlsx")

write.xlsx(saved_files, file = saved_path, rowNames = FALSE)
write.xlsx(excluded_files, file = excluded_path, rowNames = FALSE)

cat("\nPOS extraction completed.\n")
cat("POS files saved in:", output_folder, "\n")
cat("Saved file record:", saved_path, "\n")
cat("Excluded file record:", excluded_path, "\n")
```
## Check for the number of tokens
```{r}
library(stringr)
library(readr)

# Set the POS output folder
output_folder <- "D:/NLPtools/ZCTC WordSmith edition/pos1500"

# Get all POS 1500 txt files
pos_files <- list.files(
  path = output_folder,
  pattern = "_pos1500\\.txt$",
  full.names = TRUE
)

# Initialize checking result data frame
check_counts <- data.frame(
  FileID = character(),
  POSTagCount = integer(),
  stringsAsFactors = FALSE
)

# Check each POS file
for (file in pos_files) {
  
  text <- read_file(file, locale = locale(encoding = "UTF-8"))
  
  # Split POS tags by spaces
  pos_tags <- unlist(str_split(str_squish(text), "\\s+"))
  pos_tags <- pos_tags[pos_tags != ""]
  
  check_counts <- rbind(
    check_counts,
    data.frame(
      FileID = basename(file),
      POSTagCount = length(pos_tags),
      stringsAsFactors = FALSE
    )
  )
}

# Print all checking results
print(check_counts)

# Show files that are not exactly 1500 POS tags
problem_files <- check_counts[check_counts$POSTagCount != 1500, ]

print(problem_files)
```

## ZCTC POS entropy
```{r}
library(quanteda)
library(quanteda.textstats)
library(openxlsx)
library(stringr)

# Set the POS folder path
folder_path <- "D:/NLPtools/ZCTC WordSmith edition/pos1500"

# Get all POS 1500 txt files
pos_files <- list.files(
  path = folder_path,
  pattern = "_pos1500\\.txt$",
  full.names = TRUE
)

# Initialize result data frame
entropy_results <- data.frame(
  FileID = character(),
  POSentropy = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each POS file
for (file in pos_files) {
  
  # Extract file ID
  # Example: ZCTC_A01_pos1500.txt -> ZCTC_A01
  file_id <- basename(file)
  file_id <- str_replace(file_id, "_pos1500\\.txt$", "")
  
  # Read POS tag sequence
  text <- readLines(file, warn = FALSE, encoding = "UTF-8")
  text <- paste(text, collapse = " ")
  
  # Create corpus
  corpus_obj <- corpus(text)
  
  # Tokenize POS tags
  toks <- tokens(corpus_obj, remove_punct = FALSE)
  
  # Create document-feature matrix
  dfmat <- dfm(toks)
  
  # Calculate POS entropy
  entropy_val <- textstat_entropy(dfmat)$entropy
  
  # Add result
  entropy_results <- rbind(
    entropy_results,
    data.frame(
      FileID = file_id,
      POSentropy = entropy_val,
      stringsAsFactors = FALSE
    )
  )
}

# Save results to Excel
output_path <- file.path(
  folder_path,
  "ZCTC_POSentropy_results.xlsx"
)

write.xlsx(
  entropy_results,
  file = output_path,
  rowNames = FALSE
)

cat("ZCTC POS entropy calculation completed. Results saved to:", output_path, "\n")
```

# LCMC POS
## Cleaning LCMC for pos tags
```{r}
library(xml2)
library(stringr)
library(readr)
library(openxlsx)

# Set the folder path
folder_path <- "D:/NLPtools/LCMCv2 WordSmith edition"

# Get original .txt XML files
txt_files <- list.files(
  path = folder_path,
  pattern = "\\.txt$",
  full.names = TRUE
)

# Exclude files generated in previous steps
txt_files <- txt_files[
  !str_detect(txt_files, "_raw\\.txt$") &
  !str_detect(txt_files, "_clean1500\\.txt$") &
  !str_detect(txt_files, "_pos1500\\.txt$")
]

cat("Number of original txt files found:", length(txt_files), "\n")

# Set output folder
output_folder <- file.path(folder_path, "pos1500")
dir.create(output_folder, showWarnings = FALSE)

# Remove old POS output files
old_files <- list.files(
  path = output_folder,
  pattern = "_pos1500\\.txt$",
  full.names = TRUE
)

if (length(old_files) > 0) {
  unlink(old_files)
}

# Record saved files
saved_files <- data.frame(
  FileID = character(),
  POSTagCountBeforeTruncation = integer(),
  FinalPOSTagCount = integer(),
  stringsAsFactors = FALSE
)

# Record excluded files
excluded_files <- data.frame(
  FileID = character(),
  POSTagCount = integer(),
  Reason = character(),
  stringsAsFactors = FALSE
)

# Process each original txt file
for (file in txt_files) {
  
  # Extract file ID
  file_id <- tools::file_path_sans_ext(basename(file))
  
  # Set output file name
  output_file <- file.path(output_folder, paste0(file_id, "_pos1500.txt"))
  
  # Read and parse UTF-16 XML content
  xml_text_content <- read_file(file, locale = locale(encoding = "UTF-16LE"))
  
  doc <- tryCatch(
    read_xml(xml_text_content),
    error = function(e) NULL
  )
  
  if (is.null(doc)) {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = file_id,
        POSTagCount = 0,
        Reason = "XML parsing failed",
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", file_id, "- XML parsing failed\n")
    next
  }
  
  # Extract all <s> elements
  sentences <- xml_find_all(doc, ".//s")
  
  # Initialize POS tag vector
  pos_tags <- c()
  
  for (s in sentences) {
    
    # Extract sentence text
    raw <- xml_text(s)
    
    # Split sentence into word_POS tokens
    tokens <- unlist(str_split(str_squish(raw), "\\s+"))
    tokens <- tokens[tokens != ""]
    
    for (tok in tokens) {
      
      # Keep only tokens containing an underscore
      if (!str_detect(tok, "_")) {
        next
      }
      
      # Extract word and POS tag based on the last underscore
      word <- str_replace(tok, "_[^_]+$", "")
      pos <- str_extract(tok, "(?<=_)[^_\\s]+$")
      
      # Remove invalid POS tags
      if (is.na(pos) || pos == "") {
        next
      }
      
      # Remove punctuation tokens, such as ，_w and 。_w
      if (str_detect(word, "^[\\p{P}]+$")) {
        next
      }
      
      # Keep POS tag
      pos_tags <- c(pos_tags, pos)
    }
  }
  
  # Count POS tags after removing punctuation
  pos_count <- length(pos_tags)
  
  # Exclude files with fewer than 1500 POS tags
  if (pos_count < 1500) {
    excluded_files <- rbind(
      excluded_files,
      data.frame(
        FileID = file_id,
        POSTagCount = pos_count,
        Reason = "Fewer than 1500 POS tags",
        stringsAsFactors = FALSE
      )
    )
    
    cat("Excluded:", file_id, "-", pos_count, "POS tags\n")
    next
  }
  
  # Keep only the first 1500 POS tags
  pos_tags_1500 <- pos_tags[1:1500]
  
  # Save POS tags
  write_lines(paste(pos_tags_1500, collapse = " "), output_file)
  
  # Record saved files
  saved_files <- rbind(
    saved_files,
    data.frame(
      FileID = file_id,
      POSTagCountBeforeTruncation = pos_count,
      FinalPOSTagCount = length(pos_tags_1500),
      stringsAsFactors = FALSE
    )
  )
  
  cat("Saved:", file_id, "-", pos_count, "POS tags before truncation; 1500 POS tags saved\n")
}

# Save records
saved_path <- file.path(output_folder, "LCMC_saved_pos1500_files.xlsx")
excluded_path <- file.path(output_folder, "LCMC_excluded_pos_files.xlsx")

write.xlsx(saved_files, file = saved_path, rowNames = FALSE)
write.xlsx(excluded_files, file = excluded_path, rowNames = FALSE)

cat("\nPOS extraction completed.\n")
cat("POS files saved in:", output_folder, "\n")
cat("Saved file record:", saved_path, "\n")
cat("Excluded file record:", excluded_path, "\n")
```
## Check for the number of tokens
```{r}
library(stringr)
library(readr)

# Set the POS output folder
output_folder <- "D:/NLPtools/LCMCv2 WordSmith edition/pos1500"

# Get all POS 1500 txt files
pos_files <- list.files(
  path = output_folder,
  pattern = "_pos1500\\.txt$",
  full.names = TRUE
)

# Initialize checking result data frame
check_counts <- data.frame(
  FileID = character(),
  POSTagCount = integer(),
  stringsAsFactors = FALSE
)

# Check each POS file
for (file in pos_files) {
  
  text <- read_file(file, locale = locale(encoding = "UTF-8"))
  
  # Split POS tags by spaces
  pos_tags <- unlist(str_split(str_squish(text), "\\s+"))
  pos_tags <- pos_tags[pos_tags != ""]
  
  check_counts <- rbind(
    check_counts,
    data.frame(
      FileID = basename(file),
      POSTagCount = length(pos_tags),
      stringsAsFactors = FALSE
    )
  )
}

# Print all checking results
print(check_counts)

# Show files that are not exactly 1500 POS tags
problem_files <- check_counts[check_counts$POSTagCount != 1500, ]

print(problem_files)
```

## LCMC POS entropy
```{r}
library(quanteda)
library(quanteda.textstats)
library(openxlsx)
library(stringr)

# Set the POS folder path
folder_path <- "D:/NLPtools/LCMCv2 WordSmith edition/pos1500"

# Get all POS 1500 txt files
pos_files <- list.files(
  path = folder_path,
  pattern = "_pos1500\\.txt$",
  full.names = TRUE
)

# Initialize result data frame
entropy_results <- data.frame(
  FileID = character(),
  POSentropy = numeric(),
  stringsAsFactors = FALSE
)

# Loop through each POS file
for (file in pos_files) {
  
  # Extract file ID
  file_id <- basename(file)
  file_id <- str_replace(file_id, "_pos1500\\.txt$", "")
  
  # Read POS tag sequence
  text <- readLines(file, warn = FALSE, encoding = "UTF-8")
  text <- paste(text, collapse = " ")
  
  # Create corpus
  corpus_obj <- corpus(text)
  
  # Tokenize POS tags
  toks <- tokens(corpus_obj, remove_punct = FALSE)
  
  # Create document-feature matrix
  dfmat <- dfm(toks)
  
  # Calculate POS entropy
  entropy_val <- textstat_entropy(dfmat)$entropy
  
  # Add result
  entropy_results <- rbind(
    entropy_results,
    data.frame(
      FileID = file_id,
      POSentropy = entropy_val,
      stringsAsFactors = FALSE
    )
  )
}

# Save results to Excel
output_path <- file.path(folder_path, "LCMC_POSentropy_results.xlsx")

write.xlsx(
  entropy_results,
  file = output_path,
  rowNames = FALSE
)

cat("LCMC POS entropy calculation completed. Results saved to:", output_path, "\n")
```

# Merge datasets
```{r}
library(readxl)
library(dplyr)
library(openxlsx)

# Set paths
main_path <- "D:/NLPtools"

zctc_path <- "D:/NLPtools/ZCTC WordSmith edition"
lcmc_path <- "D:/NLPtools/LCMCv2 WordSmith edition"

zctc_clean_path <- file.path(zctc_path, "clean1500")
lcmc_clean_path <- file.path(lcmc_path, "clean1500")

zctc_pos_path <- file.path(zctc_path, "pos1500")
lcmc_pos_path <- file.path(lcmc_path, "pos1500")

# Read ZCTC files
zctc_genre <- read_excel(file.path(zctc_path, "ZCTC_genre_list.xlsx"))
zctc_wrd_entropy <- read_excel(file.path(zctc_clean_path, "ZCTC_clean1500_WRDentropy_results.xlsx"))
zctc_pos_entropy <- read_excel(file.path(zctc_pos_path, "ZCTC_POSentropy_results.xlsx"))

# Read LCMC files
lcmc_genre <- read_excel(file.path(lcmc_path, "LCMC_genre_list.xlsx"))
lcmc_wrd_entropy <- read_excel(file.path(lcmc_clean_path, "LCMC_clean1500_WRDentropy_results.xlsx"))
lcmc_pos_entropy <- read_excel(file.path(lcmc_pos_path, "LCMC_POSentropy_results.xlsx"))

# Keep required columns and make sure FileID is character
zctc_genre <- zctc_genre %>%
  select(FileID, Genre) %>%
  mutate(FileID = as.character(FileID))

zctc_wrd_entropy <- zctc_wrd_entropy %>%
  select(FileID, WRDentropy) %>%
  mutate(FileID = as.character(FileID))

zctc_pos_entropy <- zctc_pos_entropy %>%
  select(FileID, POSentropy) %>%
  mutate(FileID = as.character(FileID))

lcmc_genre <- lcmc_genre %>%
  select(FileID, Genre) %>%
  mutate(FileID = as.character(FileID))

lcmc_wrd_entropy <- lcmc_wrd_entropy %>%
  select(FileID, WRDentropy) %>%
  mutate(FileID = as.character(FileID))

lcmc_pos_entropy <- lcmc_pos_entropy %>%
  select(FileID, POSentropy) %>%
  mutate(FileID = as.character(FileID))

# Merge ZCTC data: keep only FileIDs appearing in all three ZCTC tables
zctc_merged <- zctc_genre %>%
  inner_join(zctc_wrd_entropy, by = "FileID") %>%
  inner_join(zctc_pos_entropy, by = "FileID") %>%
  select(FileID, Genre, WRDentropy, POSentropy)

# Merge LCMC data: keep only FileIDs appearing in all three LCMC tables
lcmc_merged <- lcmc_genre %>%
  inner_join(lcmc_wrd_entropy, by = "FileID") %>%
  inner_join(lcmc_pos_entropy, by = "FileID") %>%
  select(FileID, Genre, WRDentropy, POSentropy)

# Combine ZCTC and LCMC
final_table <- bind_rows(zctc_merged, lcmc_merged)

# Remove any rows with missing values, just in case
final_table <- final_table %>%
  filter(
    !is.na(FileID),
    !is.na(Genre),
    !is.na(WRDentropy),
    !is.na(POSentropy)
  )

# Export to Excel
output_path <- file.path(main_path, "LCMC_ZCTC_corpus.xlsx")

write.xlsx(
  final_table,
  file = output_path,
  rowNames = FALSE
)

cat("Merge completed. Results saved to:", output_path, "\n")
cat("Final number of rows:", nrow(final_table), "\n")
```
## Merge genres
```{r}
##generate new data
library(readxl)
library(dplyr)
library(openxlsx)
library(stringr)

# 读取原始数据
data <- read_excel("D:/NLPtools/LCMC_ZCTC_corpus.xlsx")

# 添加 Corpus 列
data <- data %>%
  mutate(Corpus = case_when(
    str_detect(FileID, "ZCTC") ~ "ZCTC",
    str_detect(FileID, "LCMC") ~ "LCMC",
    TRUE ~ "Unknown"
  ))

# 标准化 Genre 列
data <- data %>%
  mutate(Genre = str_trim(Genre),
         Genre = case_when(
           Genre == "Academic prose" ~ "Academic prose",
           Genre %in% c("News reportage", "News editorial", "News review") ~ "Press",
           Genre %in% c("Religious", "Skill/trade/hobby", "Popular lore", 
                        "Biography and essay", "Miscellaneous (official document, report ect)") ~ "General Prose",
           TRUE ~ "Fiction"
         ))

# 保存结果
output_path <- "D:/NLPtools/LCMC_ZCTC_corpus_cleaned.xlsx"
write.xlsx(data, file = output_path, rowNames = FALSE)
```

